---
title: "CV"
author: "Martín Jacinto"
email: mjacinto@csuchico.edu
output:
  pdf_document: 
    template: svm-latex-cv.tex
  html_document:
    df_print: paged
date: "`r format(Sys.time(), '%B %Y')`"
fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 10pt
geometry: margin=1in
jobtitle: Assistant Professor, California State University - Chico
linkcolor: black
fontawesome: yes
address: College of Behavioral and Social Sciences · Butte Hall, Room 701 · Chico, CA 95929
update: no
urlcolor: blue
---

```{r eval=FALSE, include=FALSE}
rmarkdown::render("~/Documents/GitHub/Curriculum-vitae/CV_Rmd/CV_main.Rmd", 
                  output_file="CV_mj.pdf",
                 output_dir=
                 "~/Documents/GitHub/mjacinto-website/files")
```


```{r setup, include=FALSE, eval=FALSE}

knitr::opts_chunk$set(echo=TRUE, cache = TRUE, warning = FALSE, 
                      message = FALSE)
require("knitr")
library(markdown)
```

# Education

**Ph.D. Sociology.** University of California, Irvine \hfill 2022

* Dissertation title: *Assessing the Impact of the 2008-09 Global Economic Crisis on the Structure and Dynamics of the Global Trade Network: A Network Analysis of International Trade*

* Committee: Katherine Faust, David A. Smith, Matthew C. Mahutga, David Schaefer

**M.A. Sociology.** University of California, Irvine \hfill 2016

**M.A. Latin American and Iberian Studies.** University of California, Santa Barbara \hfill 2012

**B.A. Political Science.** University of California, Santa Barbara \hfill 2009

# Areas of Specialization 

* Globalization; Economic Sociology; Inequality and Stratification; Development; Social Network Analysis; Quantitative Methods; Latin America

# Teaching Experience

### Instructor

*California State University, Long Beach* \hfill 2021-2022

* Modern Sociological Theory (in-person)
* Global Conflict and Resolution (in-person)
* Global Sociology (in-person)
* Elementary Statistics (in-person and online) 
 
*California State University, Dominguez Hills* \hfill 2018-2021

* Global Organizations and Social Processes (in-person)
* Globalization: Theory and Research (in-person)

*University of California, Irvine* \hfill 2018-2020
  
* Sociology/Anthropology 10B: Statistics and Probability, II (online) 
* Statistics Bootcamp Refresher (in-person, online) 

### Teaching Assistant

*University of California, Irvine; Department of Sociology* \hfill 2017-2020

* Graduate Statistics, I, II, III
* Statistics for Sociology, I, II, III
* Sociology of Birth, Death, and Migration
* Sociological Theory
* Introduction to Sociology
 
*University of California, Santa Barbara; Department of Spanish and Portuguese* \hfill 2011-2012

* Beginning Spanish, I, II
* Latin American and Iberian Studies

# Publications

## Under Review

- **Jacinto, Martín**. "Understanding the Impact of the 2008-2009 Global Economic Crisis on the Global North-South Divide: A Global Commodity Chain Framework and Application." (revise and resubmit at *Sociology Compass*)

- **Jacinto, Martín**. "Globalization in the Wake of the 2008-09 Global Economic Crisis: A 12 Longitudinal Network Analysis of Global Trade." 

- **Jacinto, Martín**. "The Stability of the Core-Periphery Structure to the 2008-09 Global Economic Crisis." 

- **Jacinto, Martín**. "Assessing the Interplay Between the Structure of the Global Trade Network and National Economic Productivity During the 2008-09 Global Economic Crisis."

- Gibson, C. Ben and **Martín Jacinto**. "The Convergence of Media Consensus in the 2014 Ayotzinapa Student Disappearance: A Cultural Consensus Analysis of Media Coverage.” 

## Manuscripts in Progress

- Faust, Katherine and **Martín Jacinto**. “Are there Core-Periphery Positions in Word Trade Networks? Cluster Analysis in Multi-Relational International Trade Networks, 1965-2000.”

# Pedagogical Development

### University of California, Irvine's Division of Teaching Excellence and Innovation 

**Pedagogical Fellow**  \hfill 2019-2020

> •	Facilitated interactive workshops designed to provide new Teaching Assistants (TAs) with skills and information that helped them jumpstart their teaching careers at the University of California, Irvine 

> •	Assessed fellows’ teaching performance by conducting in-class observation of their teaching then provided one-on-one consultation and feedback

> •	Worked with department director on developing an application and selection process of new Pedagogical Fellows that protected against selection bias, created an inclusive experience, and streamlined an effective interviewing process 

**DTEI Summer Fellows Program Coordinator** \hfill 2020-2021

> • Supported the university in fast-tracking the development of a pedagogical training program that prepares faculty and graduate students to effectively transition to online remote instruction 

> • Managed and supervised the pedagogical training of 50 fellows and faculty from various disciplines.

> • Assessed fellows’ teaching performance by conducting in-class observation of their teaching then provided one-on-one consultation and feedback

# Fellowships & Grants

### External 

- Alternate. Ford Foundation Pre-Doctoral Fellowship Program   \hfill 2017

- Honorable Mention. Ford Foundation Pre-Doctoral Fellowship Program \hfill 2016

- Honorable Mention. Ford Foundation Pre-Doctoral Fellowship Program \hfill 2015

### Internal

*University of California, Irvine*

- Summer Fellowship. Division of Teaching Excellence and Innovation ($5000) \hfill 2020

- University of California President's Dissertation Year Fellowship ($45,826.60) \hfill 2020

- Research Fellowship. Center for Global Peace and Conflict Studies ($1500) \hfill 2020

- Research Fellowship. Kugelman Center for Citizen Peacebuilding ($1200) \hfill 2020

- Associate Dean's Fellowship. School of Social Sciences ($6900) \hfill 2020

- Travel Grant. Graduate Division ($1000) \hfill 2019

- Research Fellowship. Kugelman Center for Citizen Peacebuilding ($1500) \hfill 2019

- Summer Research Fellowship. School of Social Sciences ($1000) \hfill 2017

- Travel Grant. Graduate Division ($1000) \hfill 2016

- Research Fellowship. Center for Global Peace and Conflict Studies ($1500) \hfill 2016

- Summer Research Fellowship. School of Social Sciences ($600) \hfill 2015

- Competitive Edge Summer Research Fellowship. Graduate Division ($5000) \hfill 2014

- Eugene Cota-Robles Diversity Fellowship. Graduate Division ($190,424) \hfill 2014

# Presentations

- "The Impact of the 2008-2009 Global Economimc Crisis on the Structure and Dynamics of the World Economy: A Network Analysis of International Trade." 
   
    * · _2021 Annual Meeting of the Pacific Sociological Association (Virtual)_
    * · _2019 Annual Meeting of the California Sociological Association (Riverside, CA)_
    * · _2018 The Center for Global Peace and Conflict Studies Conference (Irvine, CA)_
    
- "Are There Core-Periphery Positions in World Trade Networks? Cluster Analysis in Multi-Relational International Trade Networks, 1965, 1980, and 2000."

    * · _XXXVIII Sunbelt Conference (Utrecht, Netherlands)_
    
- "Interrupting the Domestic Democratic Peace: State Repression, Democracy and Social Mobilization in Latin America."

    * · _2017 Annual Meeting of the Sociological Association (Montreal,       Canada)_
    * · _2016 Annual Meeting of the Society for the Study of Social Problems (Seattle, WA)_

- "Applying Fuzzy-Set Qualitative Comparative Analysis (fsQCA) to the Study of State Violence and Neoliberal Development in Latin America."

    * · _2015 UC Irvine's Annual Associate Graduate Student Research Symposium (Irvine, CA)_
    * · _2014 UC Irvine's Competitive Edge Summer Research Symposium (Irvine, CA)_
    
- "Crisis of Democracy and Radical Social Mobilization: The Case of the 2006 APPO Movement in Oaxaca, Mexico."

    * · _2012 UC Santa Barbara's 14th Annual Lusofone and Hispanic Graduate Student (Santa Barbara, CA)_
    * · _2012 Annual Meeting of the Pacific Sociological Association (Long Beach, CA)_

# Honors and Awards
**Tom Angell Fellowship Award**. University of California Irvine \hfill 2020

> • The award recognizes one graduate student for demonstrating outstanding mentorship and commitment to diversity at UCI.
    
**Latino Excellence and Achievement Dinner (LEAD) Award**. University of California, Irvine \hfill 2018

> • Award recognizes graduate students that champion academic success amongst the Latinx community at UCI and in Orange County, CA.

# Service and Professsional Affiliations

### External (*Discipline*)

* Chair of Graduate Student Paper Competition Committee. Global Division. The Society for the Study of Social Problems 

* Student Representative. Section of Political Economy and World-System. American Sociological Association. 

* Manuscript Reviewer. *Sociological Focus*

### Internal (*Department, University,* and *Community*)

##### University of California, Irvine

* Graduate Student Coordinator. Graduate Access Preparation Program (GAPP). 
Student Outreach and Retention (SOAR) Center 
 
* Graduate Student Mentor. Summer Undergraduate Research Fellowship Program.  Graduate Division

* Humanities and Social Science Chair. Diverse Educational Community and Doctoral Experience (DECADE) Executive Student Council. Graduate Division 

* Organizer. The Know-How Sessions. Diverse Educational Community and Doctoral Experience (DECADE). Graduate Division

* Vice president of Finance. Associated Graduate Student (AGS). Office of Student Affairs

* Board Member. Graduate Student and Postdoctoral Resource Center Advisory Board. Graduate Division 

* Graduate Student Peer Mentor. Peer Mentoring Program. Department of Sociology.

#### Affiliations

* American Sociological Association
            
    * Section Membership:
              
        - · Political Economy of the World-System
       
        - · Global and Transnational Sociology
       
        - · Sociology of Development
       
        - · Mathematical Sociology
        
* Pacific Sociological Association
    
* Society for the Study of Social Problems

* Center for Network and Relational Analysis

# Skills and Technical Expertise

* Technical skills: Microsoft Office (Excel, Word, PowerPoint), SPSS, Stata, R, \LaTeX\, HTML, Tableau

* Web-based conferencing and communication platforms: Zoom, Canvas, Blackboard, Slack

* Languages: Spanish (advanced fluency in speaking and reading; intermediate fluency in writing)

#
**Updated `r Sys.Date()`**
















