\documentclass[10pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Martín Jacinto - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Martín Jacinto:  CV (Curriculum Vitae)},
            pdfauthor={Martín Jacinto},
            colorlinks=true,
            linkcolor=black,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Martín Jacinto}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Assistant Professor, California State
University - Chico}
\moveleft.5\hoffset\centerline{College of Behavioral and Social Sciences
· Butte Hall, Room 701 · Chico, CA 95929}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:mjacinto@csuchico.edu}{\nolinkurl{mjacinto@csuchico.edu}}} \hspace{1 mm}      \faGlobe \hspace{1 mm} \href{http://\url{https://martin726.github.io/mjacinto-website/}}{\tt \url{https://martin726.github.io/mjacinto-website/}}   } 

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\textbf{Ph.D.~Sociology.} University of California, Irvine \hfill 2022

\begin{itemize}
\item
  Dissertation title: \emph{Assessing the Impact of the 2008-09 Global
  Economic Crisis on the Structure and Dynamics of the Global Trade
  Network: A Network Analysis of International Trade}
\item
  Committee: Katherine Faust, David A. Smith, Matthew C. Mahutga, David
  Schaefer
\end{itemize}

\textbf{M.A.~Sociology.} University of California, Irvine \hfill 2016

\textbf{M.A.~Latin American and Iberian Studies.} University of
California, Santa Barbara \hfill 2012

\textbf{B.A. Political Science.} University of California, Santa Barbara
\hfill 2009

\hypertarget{areas-of-specialization}{%
\section{Areas of Specialization}\label{areas-of-specialization}}

\begin{itemize}
\tightlist
\item
  Globalization; Economic Sociology; Inequality and Stratification;
  Development; Social Network Analysis; Quantitative Methods; Latin
  America
\end{itemize}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{instructor}{%
\subsubsection{Instructor}\label{instructor}}

\emph{California State University, Long Beach} \hfill 2021-2022

\begin{itemize}
\tightlist
\item
  Modern Sociological Theory (in-person)
\item
  Global Conflict and Resolution (in-person)
\item
  Global Sociology (in-person)
\item
  Elementary Statistics (in-person and online)
\end{itemize}

\emph{California State University, Dominguez Hills} \hfill 2018-2021

\begin{itemize}
\tightlist
\item
  Global Organizations and Social Processes (in-person)
\item
  Globalization: Theory and Research (in-person)
\end{itemize}

\emph{University of California, Irvine} \hfill 2018-2020

\begin{itemize}
\tightlist
\item
  Sociology/Anthropology 10B: Statistics and Probability, II (online)
\item
  Statistics Bootcamp Refresher (in-person, online)
\end{itemize}

\hypertarget{teaching-assistant}{%
\subsubsection{Teaching Assistant}\label{teaching-assistant}}

\emph{University of California, Irvine; Department of Sociology}
\hfill 2017-2020

\begin{itemize}
\tightlist
\item
  Graduate Statistics, I, II, III
\item
  Statistics for Sociology, I, II, III
\item
  Sociology of Birth, Death, and Migration
\item
  Sociological Theory
\item
  Introduction to Sociology
\end{itemize}

\emph{University of California, Santa Barbara; Department of Spanish and
Portuguese} \hfill 2011-2012

\begin{itemize}
\tightlist
\item
  Beginning Spanish, I, II
\item
  Latin American and Iberian Studies
\end{itemize}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{under-review}{%
\subsection{Under Review}\label{under-review}}

\begin{itemize}
\item
  \textbf{Jacinto, Martín}. ``Understanding the Impact of the 2008-2009
  Global Economic Crisis on the Global North-South Divide: A Global
  Commodity Chain Framework and Application.'' (revise and resubmit at
  \emph{Sociology Compass})
\item
  \textbf{Jacinto, Martín}. ``Globalization in the Wake of the 2008-09
  Global Economic Crisis: A 12 Longitudinal Network Analysis of Global
  Trade.''
\item
  \textbf{Jacinto, Martín}. ``The Stability of the Core-Periphery
  Structure to the 2008-09 Global Economic Crisis.''
\item
  \textbf{Jacinto, Martín}. ``Assessing the Interplay Between the
  Structure of the Global Trade Network and National Economic
  Productivity During the 2008-09 Global Economic Crisis.''
\item
  Gibson, C. Ben and \textbf{Martín Jacinto}. ``The Convergence of Media
  Consensus in the 2014 Ayotzinapa Student Disappearance: A Cultural
  Consensus Analysis of Media Coverage.''
\end{itemize}

\hypertarget{manuscripts-in-progress}{%
\subsection{Manuscripts in Progress}\label{manuscripts-in-progress}}

\begin{itemize}
\tightlist
\item
  Faust, Katherine and \textbf{Martín Jacinto}. ``Are there
  Core-Periphery Positions in Word Trade Networks? Cluster Analysis in
  Multi-Relational International Trade Networks, 1965-2000.''
\end{itemize}

\hypertarget{pedagogical-development}{%
\section{Pedagogical Development}\label{pedagogical-development}}

\hypertarget{university-of-california-irvines-division-of-teaching-excellence-and-innovation}{%
\subsubsection{University of California, Irvine's Division of Teaching
Excellence and
Innovation}\label{university-of-california-irvines-division-of-teaching-excellence-and-innovation}}

\textbf{Pedagogical Fellow} \hfill 2019-2020

\begin{quote}
• Facilitated interactive workshops designed to provide new Teaching
Assistants (TAs) with skills and information that helped them jumpstart
their teaching careers at the University of California, Irvine
\end{quote}

\begin{quote}
• Assessed fellows' teaching performance by conducting in-class
observation of their teaching then provided one-on-one consultation and
feedback
\end{quote}

\begin{quote}
• Worked with department director on developing an application and
selection process of new Pedagogical Fellows that protected against
selection bias, created an inclusive experience, and streamlined an
effective interviewing process
\end{quote}

\textbf{DTEI Summer Fellows Program Coordinator} \hfill 2020-2021

\begin{quote}
• Supported the university in fast-tracking the development of a
pedagogical training program that prepares faculty and graduate students
to effectively transition to online remote instruction
\end{quote}

\begin{quote}
• Managed and supervised the pedagogical training of 50 fellows and
faculty from various disciplines.
\end{quote}

\begin{quote}
• Assessed fellows' teaching performance by conducting in-class
observation of their teaching then provided one-on-one consultation and
feedback
\end{quote}

\hypertarget{fellowships-grants}{%
\section{Fellowships \& Grants}\label{fellowships-grants}}

\hypertarget{external}{%
\subsubsection{External}\label{external}}

\begin{itemize}
\item
  Alternate. Ford Foundation Pre-Doctoral Fellowship Program \hfill 2017
\item
  Honorable Mention. Ford Foundation Pre-Doctoral Fellowship Program
  \hfill 2016
\item
  Honorable Mention. Ford Foundation Pre-Doctoral Fellowship Program
  \hfill 2015
\end{itemize}

\hypertarget{internal}{%
\subsubsection{Internal}\label{internal}}

\emph{University of California, Irvine}

\begin{itemize}
\item
  Summer Fellowship. Division of Teaching Excellence and Innovation
  (\$5000) \hfill 2020
\item
  University of California President's Dissertation Year Fellowship
  (\$45,826.60) \hfill 2020
\item
  Research Fellowship. Center for Global Peace and Conflict Studies
  (\$1500) \hfill 2020
\item
  Research Fellowship. Kugelman Center for Citizen Peacebuilding
  (\$1200) \hfill 2020
\item
  Associate Dean's Fellowship. School of Social Sciences (\$6900)
  \hfill 2020
\item
  Travel Grant. Graduate Division (\$1000) \hfill 2019
\item
  Research Fellowship. Kugelman Center for Citizen Peacebuilding
  (\$1500) \hfill 2019
\item
  Summer Research Fellowship. School of Social Sciences (\$1000)
  \hfill 2017
\item
  Travel Grant. Graduate Division (\$1000) \hfill 2016
\item
  Research Fellowship. Center for Global Peace and Conflict Studies
  (\$1500) \hfill 2016
\item
  Summer Research Fellowship. School of Social Sciences (\$600)
  \hfill 2015
\item
  Competitive Edge Summer Research Fellowship. Graduate Division
  (\$5000) \hfill 2014
\item
  Eugene Cota-Robles Diversity Fellowship. Graduate Division (\$190,424)
  \hfill 2014
\end{itemize}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\begin{itemize}
\item
  ``The Impact of the 2008-2009 Global Economimc Crisis on the Structure
  and Dynamics of the World Economy: A Network Analysis of International
  Trade.''

  \begin{itemize}
  \tightlist
  \item
    · \emph{2021 Annual Meeting of the Pacific Sociological Association
    (Virtual)}
  \item
    · \emph{2019 Annual Meeting of the California Sociological
    Association (Riverside, CA)}
  \item
    · \emph{2018 The Center for Global Peace and Conflict Studies
    Conference (Irvine, CA)}
  \end{itemize}
\item
  ``Are There Core-Periphery Positions in World Trade Networks? Cluster
  Analysis in Multi-Relational International Trade Networks, 1965, 1980,
  and 2000.''

  \begin{itemize}
  \tightlist
  \item
    · \emph{XXXVIII Sunbelt Conference (Utrecht, Netherlands)}
  \end{itemize}
\item
  ``Interrupting the Domestic Democratic Peace: State Repression,
  Democracy and Social Mobilization in Latin America.''

  \begin{itemize}
  \tightlist
  \item
    · \emph{2017 Annual Meeting of the Sociological Association
    (Montreal, Canada)}
  \item
    · \emph{2016 Annual Meeting of the Society for the Study of Social
    Problems (Seattle, WA)}
  \end{itemize}
\item
  ``Applying Fuzzy-Set Qualitative Comparative Analysis (fsQCA) to the
  Study of State Violence and Neoliberal Development in Latin America.''

  \begin{itemize}
  \tightlist
  \item
    · \emph{2015 UC Irvine's Annual Associate Graduate Student Research
    Symposium (Irvine, CA)}
  \item
    · \emph{2014 UC Irvine's Competitive Edge Summer Research Symposium
    (Irvine, CA)}
  \end{itemize}
\item
  ``Crisis of Democracy and Radical Social Mobilization: The Case of the
  2006 APPO Movement in Oaxaca, Mexico.''

  \begin{itemize}
  \tightlist
  \item
    · \emph{2012 UC Santa Barbara's 14th Annual Lusofone and Hispanic
    Graduate Student (Santa Barbara, CA)}
  \item
    · \emph{2012 Annual Meeting of the Pacific Sociological Association
    (Long Beach, CA)}
  \end{itemize}
\end{itemize}

\hypertarget{honors-and-awards}{%
\section{Honors and Awards}\label{honors-and-awards}}

\textbf{Tom Angell Fellowship Award}. University of California Irvine
\hfill 2020

\begin{quote}
• The award recognizes one graduate student for demonstrating
outstanding mentorship and commitment to diversity at UCI.
\end{quote}

\textbf{Latino Excellence and Achievement Dinner (LEAD) Award}.
University of California, Irvine \hfill 2018

\begin{quote}
• Award recognizes graduate students that champion academic success
amongst the Latinx community at UCI and in Orange County, CA.
\end{quote}

\hypertarget{service-and-professsional-affiliations}{%
\section{Service and Professsional
Affiliations}\label{service-and-professsional-affiliations}}

\hypertarget{external-discipline}{%
\subsubsection{\texorpdfstring{External
(\emph{Discipline})}{External (Discipline)}}\label{external-discipline}}

\begin{itemize}
\item
  Chair of Graduate Student Paper Competition Committee. Global
  Division. The Society for the Study of Social Problems
\item
  Student Representative. Section of Political Economy and World-System.
  American Sociological Association.
\item
  Manuscript Reviewer. \emph{Sociological Focus}
\end{itemize}

\hypertarget{internal-department-university-and-community}{%
\subsubsection{\texorpdfstring{Internal (\emph{Department, University,}
and
\emph{Community})}{Internal (Department, University, and Community)}}\label{internal-department-university-and-community}}

\hypertarget{university-of-california-irvine}{%
\subparagraph{University of California,
Irvine}\label{university-of-california-irvine}}

\begin{itemize}
\item
  Graduate Student Coordinator. Graduate Access Preparation Program
  (GAPP). Student Outreach and Retention (SOAR) Center
\item
  Graduate Student Mentor. Summer Undergraduate Research Fellowship
  Program. Graduate Division
\item
  Humanities and Social Science Chair. Diverse Educational Community and
  Doctoral Experience (DECADE) Executive Student Council. Graduate
  Division
\item
  Organizer. The Know-How Sessions. Diverse Educational Community and
  Doctoral Experience (DECADE). Graduate Division
\item
  Vice president of Finance. Associated Graduate Student (AGS). Office
  of Student Affairs
\item
  Board Member. Graduate Student and Postdoctoral Resource Center
  Advisory Board. Graduate Division
\item
  Graduate Student Peer Mentor. Peer Mentoring Program. Department of
  Sociology.
\end{itemize}

\hypertarget{affiliations}{%
\paragraph{Affiliations}\label{affiliations}}

\begin{itemize}
\item
  American Sociological Association

  \begin{itemize}
  \item
    Section Membership:

    \begin{itemize}
    \item
      · Political Economy of the World-System
    \item
      · Global and Transnational Sociology
    \item
      · Sociology of Development
    \item
      · Mathematical Sociology
    \end{itemize}
  \end{itemize}
\item
  Pacific Sociological Association
\item
  Society for the Study of Social Problems
\item
  Center for Network and Relational Analysis
\end{itemize}

\hypertarget{skills-and-technical-expertise}{%
\section{Skills and Technical
Expertise}\label{skills-and-technical-expertise}}

\begin{itemize}
\item
  Technical skills: Microsoft Office (Excel, Word, PowerPoint), SPSS,
  Stata, R, \LaTeX, HTML, Tableau
\item
  Web-based conferencing and communication platforms: Zoom, Canvas,
  Blackboard, Slack
\item
  Languages: Spanish (advanced fluency in speaking and reading;
  intermediate fluency in writing)
\end{itemize}

\hypertarget{section}{%
\section{}\label{section}}

\textbf{Updated 2022-06-13}

\end{document}
